How to Avoid OOTA Without Really Trying

### 2024-09-03 paper/ootavacuous.tex
asplos: Promote "Outstanding Issues" to section
And rename to "Issues and Refinements".

Perhaps later this is merged with "Future Directions".  But one step at
a time.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\subsection{Outstanding Issues}
\label{sec:Outstanding Issues}

\subsubsection{Relative versus Absolute Dependency}
\label{sec:Relative versus Absolute Dependency}

\subsubsection{Global Analysis and Volatile versus Quasi Volatile}
\label{sec:Global Analysis and Volatile versus Quasi Volatile}

\subsubsection{Effect of Memory Layout}
\label{sec:Effect of Memory Layout}

\subsubsection{Merging Quasi-Volatile Loads}
\label{sec:Merging Quasi-Volatile Loads}

@@

@@

Finally, future work might expand on
Sections~\ref{sec:Global Analysis and Volatile versus Quasi Volatile},
and~\ref{sec:Merging Quasi-Volatile Loads}
so as to more precisely delineate the limits of permissible
behavior for quasi-volatile object accesses.

>>>>

@@

\section{Issues and Refinements}
\label{sec:Issues and Refinements}

\subsection{Relative versus Absolute Dependency}
\label{sec:Relative versus Absolute Dependency}

\subsection{Global Analysis and Volatile versus Quasi Volatile}
\label{sec:Global Analysis and Volatile versus Quasi Volatile}

\subsection{Effect of Memory Layout}
\label{sec:Effect of Memory Layout}

\subsection{Merging Quasi-Volatile Loads}
\label{sec:Merging Quasi-Volatile Loads}

@@

Finally, future work might expand on
Section~\ref{sec:Issues and Refinements}
so as to more precisely delineate the limits of permissible
behavior for quasi-volatile object accesses.
